Introduction

### 2012-10-25 dissertation/tmpsolutions.tex
further partitioning most frequent objects
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@408 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

The SPLENDID paper provides a pretty clear path forward to really
solve the \langcase: Certain statistics could be amended to a new
release of VoID for cases where it very clearly would have impact. It
would be up to the data management software to identify those case
based on the work I publish.

There are two basic classes of solutions to this problem: One is to
allow further nesting of dataset partitions. VoID currently allow
class and property partitions, where the class partitions are the most
important in SPLENDID, property partitions is the most interesting for
conditional statistics. Within property partitions, one could imagine
a nested object partition, and the \langcase{} could be solved
conclusively by specifying the number of triples containing each
language. If we did the same thing with subject partitions, it would
be a very good solution to this and similar problems. However, it
would be a rather verbose solution.

The second option is based on what the database literature knows as
most-frequent-values histograms. This is a technique used by
PostgreSQL. The (over-)simplified version of this is to say in a VoID
description:

\begin{verbatim}
_:foo void:propertyPartition 
  [
    void:property dct:language ;
    void:mostFrequentObjects lang:nb .
].
\end{verbatim}
This would declare \rdfterm{lang:nb} as the most frequent object for
\rdfterm{dct:language}, and this simple example would solve the
\langcase.

While rare objects might more seldomly occur in queries, they may
contribute very significantly to the performance if they are joined
first if they do. Thus, it might be worthwhile to have a property
\rdfterm{void:leastFrequentOjects} too, as well as corresponding
properties for subjects.
